---
title: "HW 5"
author: "Hailey Cray"
date: "2/12/2020"
output: html_document
---
1. Assign to the variable n_dims a single random integer between 3 and 10.
```{r}
library(ggplot2)
```

Create a vector of consecutive integers from 1 to n_dims2.
```{r}
n_dims <- runif(1,3,10)
print(n_dims) 
# n_dims = 6.009324
my_vec <- c(1:n_dims^2)
print(my_vec)
# my_vec =  1  2  3  4  5  6  7  8  9 10 11 12 13 14 15 16 17 18 19 20 21 22 23 24 25 26 27 28 29 30 31 32 33 34 35 36
```

Use the sample function to randomly reshuffle these values.
```{r}
sample(my_vec)

# 13 20 26  3 24  1  8 29 32 18 31  7 21  9 34 19 22 33 11 17  5 15 14 36 30  4 12 27 16 25  6 35 28  2 23 10
```

create a square matrix with these elements.
```{r}
m <- matrix(nrow=n_dims,ncol=n_dims, data=my_vec)
```

print out the matrix.
```{r}
print(m)
```

find a function in r to transpose the matrix.
```{r}
t(m)
```

print it out again and note how it has changed.
```{r}
print(m)
```

calculate the sum and the mean of the elements in the first row and the last row.
```{r}
sum(m[1,]) # sum of row 1 = 96
mean(m[1,]) # mean of row 1 = 16

sum(m[3,]) # sum of row 6 = 126
mean(m[3,]) # mean of row 6 = 21
```

read about the eigen() function and use it on your matrix
```{r}
eigen(m)
eigenm <- eigen(m)
```

look carefully at the elements of $values and $vectors. What kind of numbers are these?


dig in with the typeof() function to figure out their type.
```{r}
typeof(eigenm$values) # "complex"
typeof(eigenm$vectors) # "complex"
```

if have set your code up properly, you should be able to re-run it and create a matrix of different size because n_dims will change.

2. Create a list with the following named elements:

my_matrix, which is a 4 x 4 matrix filled with random uniform values
```{r}
n_dims <- runif(16)
my_vec <- n_dims
my_matrix <- matrix(nrow = 4,ncol = 4, data=my_vec)
print(my_matrix)

# [,1]      [,2]       [,3]      [,4]
# [1,] 0.04675246 0.8698236 0.48277226 0.1212375
# [2,] 0.75057962 0.4924749 0.69944237 0.8551145
# [3,] 0.14434500 0.6099876 0.09770971 0.6012120
# [4,] 0.84660346 0.7095230 0.14105809 0.7470141
```

my_logical which is a 100-element vector of TRUE or FALSE values. Do this efficiently by setting up a vector of random values and then applying an inequality to it.
```{r}
my_logical <- runif(100)
print(my_logical)
my_logical <- my_logical[] < 0.5
print(my_logical)
```

my_letters, which is a 26-element vector of all the lower-case letters in random order.
```{r}
my_letters <- sample(letters[seq(from = 1,to = 26)])
print(my_letters)
```
```{r}
list_a <- list(my_matrix, my_logical, my_letters)
print(list_a)
```

create a new list, which has the element[2,2] from the matrix, the second element of the logical vector, and the second element of the letters vector.
```{r}
list_b <- list(list_a[[1]][2,2], list_a[[2]][2], list_a[[3]][2])
print(list_b)              
```

use the typeof() function to confirm the underlying data types of each component in this list
```{r}
typeof(list_b[[1]]) # "double"
typeof(list_b[[2]]) # "logical"
typeof(list_b[[3]]) # "character"
str(list_b)
```

combine the underlying elements from the new list into a single atomic vector with the c() function.
```{r}
vector_c <- c(list_b[[1]],list_b[[2]],list_b[[3]])
typeof(vector_c) # "character" is the data type of this vector.
```
what is the data type of this vector?
3. Create a data frame with two variables (= columns) and 26 cases (= rows).
```{r}
my_df <- data.frame("my_unis"= runif(26, min=0,max=10),"my_letters"=sample(letters[seq(from = 1,to = 26)]))
print(my_df)
```

call the first variable my_unis and fill it with a random uniform value from 0 to 10

call the second variable my_letters and fill it with 26 capital letters in random order.

for the first variable, use a single line of code in R to select 4 random rows and replace the numerical values in those rows with NA.
```{r}
library(plyr)
my_df[sample(nrow(my_df),4, replace=FALSE),1] <- NA
print(my_df)
```

for the first variable, write a single line of R code to identify which rows have the missing values.
```{r}
which(is.na(my_df))
```

for the second variable, sort it in alphabetical order
```{r}
my_df$my_letters <- sort(my_df$my_letters)
print(my_df)
# Assistance from Stack Overflow
```

calculate the column mean for the first variable.
```{r}
mean(my_df[which(is.na(my_df[,1]) == FALSE),1]) # 5.0763
           
```


