---
title: "Homework_10"
author: "Hailey Cray"
date: "4/21/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---
Part one: making a for loop to write a function that will calculate the number of zeroes in my numeric vector.
```{r setup, include=FALSE}
# ----------------------------------
# FUNCTION count_my_zeroes
# description: this function calculates the number of zeroes in a numeric vector.
# inputs: a numeric vector
# outputs: the number of zeroes in the vector.
####################################
count_my_zeroes <- function(vec=sample(0:9, 100, replace=TRUE)) {
  counter <- 0
  for(i in 1:length(vec)) {
    if(vec[i] < 1) {
      counter <- counter+1
    }
  }  

return(counter)

} 
# setting up my function for the vector that I am using to count my number of zeroes

# end of count_my_zeroes
# ----------------------------------
# Testing my coding to see if it worked:
trying_forloop <- sample(0:9, 100, replace =TRUE)
count_my_zeroes(vec=trying_forloop)
print(trying_forloop)
```
Part 2: Now to use subsetting instead of a for loop: 
```{r}
# ----------------------------------
# FUNCTION subset_count_my_zeroes
# description: The subsetted version of the function count_my_zeroes to count the number of zeroes occuring in a numeric vector. 
# inputs: my numeric vector from above
# outputs: the number of zeroes in the vector
####################################
subset_count_my_zeroes <- function(vec=sample(0:9, 100, replace= TRUE)) {
  
  count_zeroes <- length(which(vec ==0))
  
  return(count_zeroes)

} # end of subset_count_my_zeroes
subset_count_my_zeroes()
# ----------------------------------

```
Part 3: writing a function with input = two integers representing the number of rows and columns in a matrix. The matrix will be the output of these dimensions where each element is the product of row number * column number.
```{r}
# ----------------------------------
# FUNCTION my_matrix
# description:making my matrix where each element filling the matric is the product of row # * column #.
# inputs: nrow number and ncol number
# outputs: my_matrix with elements calculated by nrow * ncol. 
####################################
my_matrix <- function(nrow=5, ncol=5) {

  matrix_p3 <- matrix(nrow= nrow, ncol= ncol)
  for(i in 1:nrow) {
    for(j in 1:ncol) {
      matrix_p3[i,j] <- i * j
    }
  }  

return(matrix_p3)

} # end of my_matrix
# ----------------------------------
my_matrix(nrow=10, ncol=12)
```
Part 4: doing a randomization test for my own data.
```{r}
# Getting my necessary libraries loaded in
library(ggplot2)

# I am using systolic blood pressure measurement from n=25 smokers and n=25 non-smokers. Total sample is n=50.
set.seed(50)

# ----------------------------------
# Making data frame bp_df with 2 columns: number of packs of cigarettes smoked per day and 25 rows of systolic blood pressure measurements ranging from 110 to 180 mm Hg. 
####################################

```
```{r}
# ----------------------------------
# FUNCTION get_data
# description:bring in data for analysis
# inputs: file name
# outputs: 2 column data frame of data: smoker status (as 0 or 1) and systolic blood pressure measurement in mm Hg. 
####################################

file_name <- "Homework_10_bp_data.csv"
get_data <- function(z=file_name) {
  my_df <- read.table(file=z,
                    header=FALSE,
                    stringsAsFactors = FALSE, 
                    sep=",")
print(my_df)
}
bp_data <- get_data()

# end of get_data
# ----------------------------------
# FUNCTION calc_anova
# description: drawing down from above: bringing in data from get_data function
# inputs: data from above chunk: bringing down my_df as a data frame from get_data function
# outputs: ANOVA for smokers vs nonsmokers blood pressure (systolic)
####################################: 
# ano_model <- aov(res_var~t_group, data=ano_data)
calc_anova <- function(data=bp_data) {
  
ano_bp <- aov(V1~V2, data=bp_data)
# calling data from above
summary(ano_bp)
 }

calc_anova()

 # end of: calc_anova
# ----------------------------------

# ----------------------------------
# FUNCTION reshuffle_data
# description: randomizing data 
# inputs: my_df
# outputs: reshuffled my_df
####################################
reshuffle_data <- function(z=NULL) {
  if(is.null(z)){
    x_obs <- rbinom(50, 1, 0.5)
    y_obs <- sample(80:180,50, replace=TRUE)
    z <- data.frame(x_obs, y_obs) }
  shuffled_df <- z

return(shuffled_df)

} 
shuffled_data <- reshuffle_data()
print(shuffled_data)
# end of reshuffle_data
# ----------------------------------

# ----------------------------------
# FUNCTION shuffle_anova
# description: generate a p-value for significance for shuffled data
# inputs: shuffled_data
# outputs: my p-value for the randomized data 
####################################
shuffle_anova <- function(data=shuffled_data) {
  
ano_shuffle <- aov(x_obs~y_obs, data=shuffled_data)
# calling data from above
summary(ano_shuffle)
 }

shuffle_anova()
 # end of get_sig
sig_shuffle <- shuffle_anova()
print(sig_shuffle)
# ----------------------------------
```
The p-value calculated for my real data was 0.00116: 
Df Sum Sq Mean Sq F value
t_group      1   2718  2718.3   11.94
Residuals   48  10929   227.7        
             Pr(>F)   
t_group     0.00116 **
This was significant, as expected. We know that people who smoke generally have a higher blood pressure than non-smokers. 

For my randomized (reshuffled) data, this relationship between smoking status and blood pressure was no longer significant: the p-value was 0.366.
 Df Sum Sq Mean Sq F value Pr(>F)
y_obs        1  0.212  0.2122   0.834  0.366
Residuals   48 12.208  0.2543   

So now if I run the code again with different values using the set.seed function to see what my shuffled p-value is, I get p = 0.933. When I run it one more time with different values, my p-value = 0.174. I'm continuously getting non-signficant p-values, which suggests that there is actually a relationship between systolic blood pressure and smoking status in my original data. It's highly unlikely that I'll get positive smoking status lined up with high blood pressure readings when I randomly reshuffle the data, which lends support to my hypothesis that positive (present) smoking status contributes to higher systolic blood pressure. 








