---
title: "Homework_8"
author: "Hailey Cray"
date: "3/4/2020"
output: html_document
---
Homework #8: data manipulations using the dplyr package
```{r}
library(dplyr)
data(iris)
```


Structure of iris: 
```{r}
class(iris)
glimpse(iris)
```
The iris dataset is a data frame and has 150 observations and 5 variables (Sepal.Length, Sepal.Width, Petal.Length, Petal.Width, and Species)


```{r}
iris1 <- filter(iris, Species %in% c("virginica", "versicolor"), Sepal.Length>6, Sepal.Width>2.5)
glimpse(iris1)
```
Now there are 56 observations but there are still 5 variables in the new iris1 data set. 


```{r}
iris2 <- select(iris1, Species, Sepal.Length, Sepal.Width)
glimpse(iris2)
```
iris2 now has 3 variables (Species, Sepal.Length, and Sepal.Width) and 56 observations.

Create an iris3 data frame from iris2 that orders the observations from largest to smallest sepal length. Show the first 6 rows of this dataset.
```{r}
iris3 <- arrange(iris2, by=desc(Sepal.Length))
head(iris3)
```


```{r}
iris4 <- mutate(iris3, Sepal.Area = Sepal.Length*Sepal.Width)
glimpse(iris4)
```
iris4 has 4 variables (Species, Sepal.Length, Sepal.Width, and Sepal.Area) and 56 observations. 


```{r}
iris5 <- mutate(iris4, meanSepal.Length = mean(Sepal.Length), meanSepal.Width = mean(Sepal.Width), Sample_Size = n())
print(iris5)
```


```{r}
  iris6 <- group_by(iris4, Species) 
  iris6 <- mutate(iris4, meanSepal.Length = mean(Sepal.Length), meanSepal.Width = mean(Sepal.Width), Sample.Size=n()) 
 print(iris6)
```

Piping from iris to iris6: 
```{r}
iris %>%
  filter(Species %in% c("virginica", "versicolor"), Sepal.Length>6, Sepal.Width>2.5) %>%
  select(Species, Sepal.Length, Sepal.Width) %>%
  arrange(by=desc(Sepal.Length)) %>%
  mutate(Sepal.Area = Sepal.Length*Sepal.Width) %>%
  group_by(Species) %>%
  mutate(meanSepal.Length = mean(Sepal.Length), meanSepal.Width = mean(Sepal.Width), Sample.Size=n())
  
  
  
  
  
  
  

  






```

