---
title: "Homework_10"
author: "Hailey Cray"
date: "4/21/2020"
output: html_document
---
Part one: making a for loop to write a function that will calculate the number of zeroes in my numeric vector.
```{r setup, include=FALSE}
# ----------------------------------
# FUNCTION count_my_zeroes
# description: this function calculates the number of zeroes in a numeric vector.
# inputs: a numeric vector
# outputs: the number of zeroes in the vector.
####################################
count_my_zeroes <- function(vec=sample(0:9, 100, replace=TRUE)) {
  counter <- 0
  for(i in 1:length(vec)) {
    if(vec[i] < 1) {
      counter <- counter+1
    }
  }  

return(counter)

} 
# setting up my function for the vector that I am using to count my number of zeroes

# end of count_my_zeroes
# ----------------------------------
# Testing my coding to see if it worked:
trying_forloop <- sample(0:9, 100, replace =TRUE)
count_my_zeroes(vec=trying_forloop)
print(trying_forloop)
```
Part 2: Now to use subsetting instead of a for loop: 
```{r}
# ----------------------------------
# FUNCTION subset_count_my_zeroes
# description: The subsetted version of the function count_my_zeroes to count the number of zeroes occuring in a numeric vector. 
# inputs: my numeric vector from above
# outputs: the number of zeroes in the vector
####################################
subset_count_my_zeroes <- function(vec=sample(0:9, 100, replace= TRUE)) {
  
  count_zeroes <- length(which(vec ==0))
  
  return(count_zeroes)

} # end of subset_count_my_zeroes
subset_count_my_zeroes()
# ----------------------------------

```
Part 3: writing a function with input = two integers representing the number of rows and columns in a matrix. The matrix will be the output of these dimensions where each element is the product of row number * column number.
```{r}
# ----------------------------------
# FUNCTION my_matrix
# description:making my matrix where each element filling the matric is the product of row # * column #.
# inputs: nrow number and ncol number
# outputs: my_matrix with elements calculated by nrow * ncol. 
####################################
my_matrix <- function(nrow=5, ncol=5) {

  matrix_p3 <- matrix(nrow= nrow, ncol= ncol)
  for(i in 1:nrow) {
    for(j in 1:ncol) {
      matrix_p3[i,j] <- i * j
    }
  }  

return(matrix_p3)

} # end of my_matrix
# ----------------------------------
my_matrix(nrow=10, ncol=12)
```
Part 4: doing a randomization test for my own data.
```{r}
# Getting my necessary libraries loaded in
library(ggplot2)

# I am using systolic blood pressure measurement from n=25 smokers and n=25 non-smokers. Total sample is n=50.
set.seed(50)

# ----------------------------------
# Making data frame bp_df with 2 columns: number of packs of cigarettes smoked per day and 25 rows of systolic blood pressure measurements ranging from 110 to 180 mm Hg. 
####################################

```
```{r}
# ----------------------------------
# FUNCTION get_data
# description:bring in data for analysis
# inputs: file name
# outputs: 2 column data frame of data: smoker status (as 0 or 1) and systolic blood pressure measurement in mm Hg. 
####################################

z <- NULL
get_data <- function(z=NULL) {

if(is.null(z)) {
  x_obs <- rbinom(50, 1, 0.5)
  y_obs <- sample(80:180,50, replace=TRUE)
  my_df <- data.frame(x_obs,y_obs)
}
  my_df <- read.csv(file=z,
                    header=TRUE,
                    stringsAsFactors = FALSE)
return(print(my_df))
print(my_df)
}

# end of get_data
# ----------------------------------


# ----------------------------------
# FUNCTION get_slope
# description: calculating slope of randomization test
# inputs: data frame my_df with 2 columns: 1 or 0 (1 is smoker, 0 is non-smoker) and systolic blood pressure in mmHg for 50 individuals
# outputs: slope for regression analysis
####################################
function_name <- function(z=NULL) {
  if(is.null(z)){
    x_obs <- rbinom(50, 1, 0.5)
    y_obs <- sample(80:180,50, replace=TRUE)
    z <- data.frame(x_obs,y_obs) }
  for(i in 1:nrow(z)) {
    ifelse(z[i,0] == "Non-Smoker", z[i,10 <- "Smoker" 
  z <- lm(z[1]~z[2])
  z <- summary(z)
  z <- z$coefficients[1,2]
  slope_bp <- z
  return(slope) }


} # end of function_name
# ----------------------------------
# ASK LAUREN ABOUT WHY IT TELLS ME THAT THERE IS AN ERROR IN 1:nrow(z): argument of length 0


# ----------------------------------
# FUNCTION reshuffle_data
# description: randomizing data 
# inputs: my_df
# outputs: reshuffled my_df
####################################
reshuffle_data <- function(z=NULL) {
  if(is.null(z)){
    x_obs <- rbinom(50, 1, 0.5)
    y_obs <- sample(80:180,50, replace=TRUE)
    z <- data.frame(x_obs, y_obs) }
  shuffled_df <- z

return(shuffled_df)

} # end of reshuffle_data
# ----------------------------------
print(shuffled_df)

# ASK LAUREN: RETURNS A NULL STATEMENT



# ----------------------------------
# FUNCTION get_sig
# description: generate a p-value for significance
# inputs: summary of my slope and coefficients, my simulated vector, reshuffled
# outputs: my p-value, 
####################################
get_sig <- function(z=NULL) {
  if(is.null(z)) {
    z <- 
# NOT SURE HOW TO DO THIS

# Function body

return("Checking...get_sig")

} # end of get_sig
# ----------------------------------

  
# ----------------------------------
# FUNCTION scatterplot_bp
# description: scatterplot of smoker status vs systolic blood pressure using the simulated "fake" values
# inputs: my real metric vs simulated metric
# outputs: scatterplot
####################################
scatterplot_bp <- function(z=NULL) {
  if(is.null(z)) {
    z <- 
      
  my_df1 <- data.frame(SmokerYN=seq_along(z[[1[[), 
  




} # end of scatterplot_bp
# ----------------------------------
# Bringing in my own data: 
  n_sim <- 100 # 100 reps
  x_sim <- rep(NA, n_sim) # an empty vector for simulated slopes. Sophie Kogut helped with this code.
  
  my_df2 <- get_data(z="/Users/HaileyCray/iCloud/Desktop/Homework_10_bp_data.csv")

x_obs <- get_slope(z=my_df1)
for (i in seq_len(n_sim)) {
  x_sim[i] <- get_slope(reshuffle_data(my_df1))
}
slope1 <- list(x_obs, x_sim)
p_vals <- get_sig(slope1)

scatterplot_bp(slope1)

```

