---
title: "Homework_6"
author: "Hailey Cray"
date: "2/19/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(ggplot2) 
library(MASS) 
# ggplot is called for the graphics, and MASS is called for maximum likelihood estimations.
```

 

Now the data on systolic blood pressure are called. 
```{r}
z <- read.table("/Users/HaileyCray/Desktop/SysBP.csv",header=TRUE,sep=",",stringsAsFactors=FALSE)
str(z)
summary(z)
```


```{r}
# z <- rnorm(n=25,mean=132.5)
# z <- data.frame(1:3000,z)
# names(z) <- list("Patient_ID","Sys_BP")
# z <- z[z$myVar>0,]
# str(z)
# summary(z$myVar)
# This is for "fake" data. 
```


```{r}
# Then this systolic blood pressure data from 25 pregnant indivuduals is plotted in a simple histogram. 
p1 <- ggplot(data=z, aes(x=Sys_BP, y=..density..)) +
  geom_histogram(color="orchid",fill="aquamarine2",size=0.2) 
print(p1)
```

```{r}
# Then an empirical density curve is added to the histogram to smooth out the shape. 
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)

```


```{r}
# Now a normal distribution is fit to these data. The maximum likelihood estimators of the two parameters of the normal distribution for the mean and the variance are grabbed. 
normPars <- fitdistr(z$Sys_BP,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] 
# note structure of getting a named attribute
```

 
```{r}
# Next, the normal probability density was plotted.
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]

xval <- seq(0,max(z$Sys_BP),len=length(z$Sys_BP))

 stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Sys_BP), args = list(mean = meanML, sd = sdML))
 p1 + stat
```

```{r}
# Then the exponential probability density was plotted. 
expoPars <- fitdistr(z$Sys_BP,"exponential")
rateML <- expoPars$estimate["rate"]

stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$Sys_BP), args = list(rate=rateML))
 p1 + stat + stat2
 
```

```{r}
# Following that, the uniform probability density of the data was plotted using the minimum and maximum of the data as the parameters. 
stat3 <- stat_function(aes(x = Sys_BP, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$Sys_BP), args = list(min=min(z$Sys_BP), max=max(z$Sys_BP)))
 p1 + stat + stat2 + stat3
```

The gamma probability density was plotted: 
```{r}
gammaPars <- fitdistr(z$Sys_BP,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]

stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$Sys_BP), args = list(shape=shapeML, rate=rateML))
 p1 + stat + stat2 + stat3 + stat4
```
4. The gamma distribution fit the systolic blood pressure data the best. In a gamma distribution, the maximum likelihod parameters are: 
```{r}
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]
print(shapeML)
print(rateML)
```
5. The maxiumum likelihood parameters in the gamma distribution are shape: 43.7206 and rate: 0.3299181. 
```{r}
# Creating simulated blood pressure data set
sim <-rgamma(n=25, shape=shapeML, rate=rateML)
sim <- data.frame(sim)
print(sim)
p3 <- ggplot(data=sim, aes(x=sim, y=..density..)) +
  geom_histogram(color="orchid",fill="aquamarine2",size=0.2)
print(p3)
# Adding probability density curve
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]
xval <- seq(0,max(sim),length=nrow(sim))
staty <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="royal blue", n = nrow(sim), args = list(shape=shapeML, rate=rateML))
p3 + staty
```

The model is doing a decently good enough job of simulating real systolic blood pressures. However, I think the simulated data tends toward the lower blood pressure range than my data, which is likely more reflective of a population. Blood pressures tend to be closer to the 120+ range rather than the 100-110 range. It seems that the simulated data's participants are healthier than the real population, which seemed to be in the hypertensive category.  


```{r}
# Lastly, the beta probability density was plotted. 
pSpecial <- ggplot(data=z, aes(x=Sys_BP/(max(Sys_BP + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Sys_BP/max(z$Sys_BP + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]

statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$Sys_BP), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

